---
title: "week10_taskset"
author: "Annabella Ritzau"
format: html
execute:
  echo: true
  warning: true
  message: true
---

#### Q1: Load and Inspect Data ------------------------------------

```{r}
## Load the saved dataset
# Save the experiment_data you have as a file
dir.create("data/raw", recursive = TRUE, showWarnings = FALSE)

# Save the file
saveRDS(experiment_data, "data/raw/experiment_data.rds")

# Confirm it worked
list.files("data/raw")
#Used Ai because experiment_data was not in my raw files, had an effect on the rest of the code
experiment_data <- readRDS("../data/raw/experiment_data")

## Take a quick look at the first few rows
head(experiment_data)

## Check the structure of the dataset
str(experiment_data)
```





```{r}
## Generate one or more random numbers between min and max (defaults: one number between 1–10)
getRandomNumber <- function(min = 1, max = 10, number = 1) {
  sample(min:max, number)
}
```

```{r}
## Classify reaction times into "Fast", "Slow", or "Unknown" (default threshold = 500ms)
## code
#function
classify_rt <- function(rt, threshold = 500) {
  if (!is.numeric(threshold) || length(threshold) != 1) {
    print("Error: 'threshold' must be a single numeric value.")
  } else
    
  if (!is.numeric(rt)) {
    print("Error: 'rt' must be numeric.")
  } 

  category <- ifelse(is.na(rt), "Unknown",
                     ifelse(rt < threshold, "Fast", "Slow"))
return(category)
}

```

#### Q3: Loops vs. Vectorization comparison to create new data----------
```{r}
#create a new age column with a NA values
experiment_data$age <- NA
#creates age in the experiment_data data-frame

for (i in 1:nrow(experiment_data)) {
  experiment_data$age[i] <- getRandomNumber(min = 18, max = 65, number = 1)
}
##nearly got it right but missed on the [i] which AI pointed out loops i from 1 to the number of rows
experiment_data$age <- sample(18:65, size = nrow(experiment_data), replace = TRUE)
                              
#loop i from one to the number of rows, minis 18 and max is 65

head(experiment_data)
```

####Applying conditionals to loops with vectorized functions
#Empty column
```{r}
experiment_data$rt_category_loop <-NA
for (i in 1:nrow(experiment_data)) {
  experiment_data$rt_category_loop[i] <- classify_rt(experiment_data$rt[i])
}

```

#Vectorized version(quicker)
```{r}
experiment_data$rt_category_vec <- classify_rt(experiment_data$rt)
```


```{r}
table(loop = experiment_data$rt_category_loop,
      vec  = experiment_data$rt_category_vec,
      useNA = "ifany")
```

####Debugging function: Is there any bugs

```{r}
## Create Buggy Function
threshold <- 500
##wasnt sure if flag was the correct variable but i saw it on the notes?

#flag_fast <- function(rt_vector) {
#  rt_vector < threshold
#}
#call the output- is it above 500 or below, flase=slow and true=quick

#fixed version
flag_fast <- function(rt_vector, threshold = 500) {
  rt_vector < threshold
}

flag_fast(experiment_data$rt)
rm(threshold)
```

####Debugging Tools in Action-finding out why a group mean is NA
```{r}
means <- tapply(experiment_data$rt,
                        experiment_data$condition,
                        mean,
                        na.rm = TRUE)
print(paste("Mean for control:", subject_means["control"]))
print(paste("Mean for incongruent:", subject_means["incongruent"]))
# How many NAs overall?
sum(is.na(experiment_data$rt))

# How many NAs by condition?
tapply(is.na(experiment_data$rt), experiment_data$condition, sum)

# Optional: quick sanity checks
summary(experiment_data$rt)
with(experiment_data, table(condition, is.na(rt)))
```
####q7: Using Ai for debugging or refactoring (will intentionally create a small bug)
```{r}
#bug
experiment_data$rt <- c("450", "520", "NA", "480")
#fixed
experiment_data$rt <- c(450, 520, 480, 500, 510, 495, 470, 530, 505, 490)
##Ai was really good at breaking down the prompt and explaining what went wrong and then instead of giving me the code it explained what went wrong and what i can do to improve the code. It worked quite well.

experiment_data$rt_category <- ifelse(experiment_data$rt < 500, "Fast", "Slow")
```


####Question 8: Saving and reloading objects----
```{r}
write.csv(
  x = experiment_data,
  file = "data/cleaned/my_cleaned_data.csv",
  row.names = FALSE
)
```
```{r}
saveRDS(
  object = experiment_data, 
  file = "data/cleaned/experiment_data.rds"
)

```


```{r}

reloaded_rds <- readRDS("data/cleaned/experiment_data.rds")

reloaded_csv <- read.csv("data/cleaned/experiment_data.csv")


```











